\prefacesection{Acknowledgements}
I would like to thank:
\begin{itemize}
  \item the Campinas State University for providing the institutional support for this study;
  \item the Rio de Janeiro State University for the cooperation with Campinas State University in their high-energy physics program. This was a key factor for this study;
  \item the HEPGRID - High Energy Physics GRID (CMS computing cluster of Rio de Janeiro State University) for providing the computing resources;
  \item the Ministry of Science, Technology and Innovation” and the “National Council for Scientific and Technological Development – CNPq”;
  \item the European Laboratory for Particle Physics (CERN) for the construction and operation of the Large Hadron Collider (LHC);
  \item the Compact Muon Solenoid (CMS) collaboration for the construction, operation and provision of the instrumental means for this study;
  \item my colleagues from CMS-RPC, specially Mehar, Jan, Andres, Nicolas, Gabriella, Mapse and Kevin. Such welcome environment, created a lot of learning opportunities, which I will take for life;
  \item my colleagues from Rio de Janeiro University, specially my friends, Eliza, Sandro, Dilson and Sheila. This work is gladly shared with them;
  \item my advisor, Prof. José Augusto Chinellato. His kindness, guidance and trust in my work made this a reality. I will thankfully take his lessons to my carrier;
  \item my co-advisor, Prof. Alberto Santoro, with all my admiration for his successful carrier and achievements as scientist. My pleasure to be his friend;
  \item my wife, Yasmin, for her love, unrestricted support and dedication. Without her, this study would never be possible;
  \item my mother, Doralice, for her unconditional love, support and inspiration.
\end{itemize}

